Multiphysics Reactor-core Simulations Using the Improved Quasi-Static Method

### 2018-09-20 doc/Papers/IQS_convergence/IQS_convergence.tex
Adding spatial profile of error for LRA

The LRA benchmark is a two-dimensional, two-group neutron diffusion problem.  
It is a super prompt-critical transient. The equations being solved are explicitly defined in problem 14-A1 of the ANL Benchmark Problem Book \cite{ANL_BPB}. The execution of the benchmark was performed by the Rattlesnake/MOOSE framework at Idaho National Laboratory (INL) \cite{wang2013}.  The spatial discretization uses continuous finite elements with first-order Lagrangian basis functions. The mesh consists of blocks $11\times 11$ with five uniform refinements, totaling $165,165$ elements and $124,609$ nodes. Three different temporal solution techniques are used: implicit discretization of the flux equations, IQS formulation, and \iqspc. Crank-Nicolson time discretization scheme is used for the space-time equations. 
The performance of IQS with temperature feedback is assessed by comparing the solution accuracy at peak power.

@@

>>>>

The LRA benchmark is a two-dimensional, two-group neutron diffusion problem.  
It is a super prompt-critical transient. The equations being solved are explicitly defined in problem 14-A1 of the ANL Benchmark Problem Book \cite{ANL_BPB}. The execution of the benchmark was performed by the Rattlesnake/MOOSE framework at Idaho National Laboratory (INL) \cite{wang2013}.  The spatial discretization uses continuous finite elements with first-order Lagrangian basis functions. The mesh consists of blocks $11\times 11$ with five uniform refinements, totaling $123,904$ elements and $124,609$ nodes. Three different temporal solution techniques are used: implicit discretization of the flux equations, IQS formulation, and \iqspc. Crank-Nicolson time discretization scheme is used for the space-time equations. 
The performance of IQS with temperature feedback is assessed by comparing the solution accuracy at peak power.

@@

All the values for error in this section are errors in the globally integrated flux. However, it is noteworthy to compare the spatial dependence of error. \fig{fig:lra_block} shows the difference in normalized power at each block of the LRA geometry for each method. The resulting spatially dependent error is in general an order of magnitude lower for IQS and IQS P-C than implicit discretization. This observation corresponds well with the globally integrated flux errors shown in Tables \ref{tab:ndiff_lra}-\ref{tab:iqspc_lra}.

\begin{figure}[htbp!]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[every node/.style = {font=\normalsize}]

\node[inner sep=0pt, anchor=south](fig) at (0,0) {\includegraphics[height=5in]{figures/lra_block.png}};
\node[rectangle, draw, align=center,anchor=north east, style={font=\footnotesize}] (des) at (1,0) {\textbf{Normalized Power (Ref.)} \\ Difference (IQS) - $\Delta t = 0.004, \ N_T = 4$ \\ Difference (IQS P-C) - $\Delta t = 0.004, \ N_T = 4$ \\ Difference (Implicit Dis.) - $\Delta t = 0.004$};
\node[anchor= north west] (dif) at (1,0) {Difference $= \frac{\text{Power}^\text{ref} - \text{Power}}{\text{Power}^\text{ref}}$};

\end{tikzpicture}%
}
\caption{Difference in normalized power from reference solution for each fissile block of LRA geometry}
\label{fig:lra_block}
\end{figure}

### 2018-09-20 doc/Papers/IQS_convergence/reviewer_notes.tex
Adding spatial profile of error for LRA

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx,amsmath, amssymb, amsthm, amsfonts,subcaption}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{float}

@@

\item[\fix] \hard{ LRA and TREAT only compare errors computed with the peak powers. Peak powers are an integral quantity and may favor IQS over spatial kinetics. The authors should also compare power distributions or similar distributed quantities. }
\begin{itemize}
\item This would require a rerun of all simulations. There is a postprocessor in MOOSE that could do it, but the simulations would be ridiculously tedious.
\end{itemize}

@@

\item[\fix] \easy{ LRA benchmark: the number of elements makes no sense 11x11 = 121 and when using five uniform refinement steps one would end up with 123,904 elements. }
\begin{itemize}
\item  Not sure how we got these numbers, but he's right
\end{itemize}

>>>>

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx,amsmath, amssymb, amsthm, amsfonts,subcaption}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{float}
\usepackage{tikz}

@@

\item[\done] \hard{ LRA and TREAT only compare errors computed with the peak powers. Peak powers are an integral quantity and may favor IQS over spatial kinetics. The authors should also compare power distributions or similar distributed quantities. }
\begin{itemize}
\item All the values for error in this section are errors in the globally integrated flux. However, it is noteworthy to compare the spatial dependence of error. Fig. 18 shows the difference in normalized power at each block of the LRA geometry for each method. The resulting spatially dependent error is in general an order of magnitude lower for IQS and IQS P-C than implicit discretization. This observation corresponds well with the globally integrated flux errors shown in Tables 6-8. 
\end{itemize}
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[every node/.style = {font=\normalsize}]
\node[inner sep=0pt, anchor=south](fig) at (0,0) {\includegraphics[height=5in]{figures/lra_block.png}};
\node[rectangle, draw, align=center,anchor=north east, style={font=\footnotesize}] (des) at (1,0) {\textbf{Normalized Power (Ref.)} \\ Difference (IQS) - $\Delta t = 0.004, \ N_T = 4$ \\ Difference (IQS P-C) - $\Delta t = 0.004, \ N_T = 4$ \\ Difference (Implicit Dis.) - $\Delta t = 0.004$};
\node[anchor= north west] (dif) at (1,0) {Difference $= \frac{\text{Power}^\text{ref} - \text{Power}}{\text{Power}^\text{ref}}$};

\end{tikzpicture}%
}

@@

\item[\done] \easy{ LRA benchmark: the number of elements makes no sense 11x11 = 121 and when using five uniform refinement steps one would end up with 123,904 elements. }
\begin{itemize}
\item  Fixed it to 123,904 elements, number of nodes was originally correct
\end{itemize}
